An assessment of statistical guidance for authors at influential academic journals across scientific disciplines: Preliminary analysis

### 2021-08-24 analysis/preliminaryAnalysis.Rmd
Create gtsummary demo

```{r load_packages}
library(knitr) # for literate programming
library(papaja) # for article template
library(tidyverse) # for data munging
library(tidylog) # inline analysis feedback
library(here) # for finding files
library(gtsummary) # for summary tables
library(lemon) # to have axes across all graph facets
library(ggthemr) # for ggplot theme
library(ggrepel) # for ggplot text labels
library(scales) # to wrap text on axis labels
```

@@

```{r tbl_counts_props}
d_all %>%

@@

  select(esi_field, starts_with("has_")) %>% 
  gtsummary::tbl_summary(
    by = esi_field,
      # statistic = list(everything() ~ "{p}% ({n} / {N})")
  ) %>%
  add_overall %>% 
  modify_footnote(everything() ~ NA) %>% 
  modify_caption("**Number and percentage of journals overall and by scientific discipline providing internal statistical guidance by topic.** Denominator for all proportions is the number of journals in the field, regardless of whether the journal has internal guidance.")
```

>>>>

```{r load_packages}
library(knitr) # for literate programming
library(papaja) # for article template
library(tidyverse) # for data munging
library(tidylog) # inline analysis feedback
library(here) # for finding files
library(gtsummary) # for summary tables note: use dev version `remotes::install_github("ddsjoberg/gtsummary")`
library(lemon) # to have axes across all graph facets
library(ggthemr) # for ggplot theme
library(ggrepel) # for ggplot text labels
library(scales) # to wrap text on axis labels
```

@@

```{r tbl_counts_props}
tbl_counts_props <-
d_all %>%

@@

  select(esi_field, starts_with("has_")) %>% 
  gtsummary::tbl_summary(
    by = esi_field,
      # statistic = list(everything() ~ "{p}% ({n} / {N})")
  ) %>%
  add_overall %>% 
  modify_footnote(everything() ~ NA) %>% 
  modify_caption("**Number and percentage of journals overall and by scientific discipline providing internal statistical guidance by topic.** Denominator for all proportions is the number of journals in the field, regardless of whether the journal has internal guidance.")

tbl_counts_props
```

## {gtsummary} in-text demo

> Overall stats are in the `stat_0` column, which is not accessible in the current release of {gtsummary}, so hence use the dev version: `remotes::install_github("ddsjoberg/gtsummary")`.

You can see that around half (`r inline_text(tbl_counts_props, variable = has_guidance, column = stat_0, pattern = "{p}")`%) of journals offered any statistical guidance. Note that this includes `r only_ext` journals which only referred to statistical guidance in external sources (reporting guidelines or academic papers). Just over quarter of journals had a dedicated statistical guidance section of their author instructions (`r inline_text(tbl_counts_props, variable = has_internal_guidance_section, column = stat_0, pattern = "{p}")`%). In two fields (Computer Science and Maths), no journals offered any statistical guidance. Journals in health-related fields were more likely to offer statistical guidance and have dedicated statistical guidance sections. Notably, 100% of the journals in clinical medicine offered some statistical guidance.
